Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-09-21 paper/uist_2016/paper.tex
fix some formatting bugs

% heather - need to be rephrased perhaps? Should we give a high level summary of all the relationships we've found? More analysis to be done for photo vs. videos, another table?
% semantic vs episodic memory
% mention distance categories in the beginning (up up up) + everything else 
\section{Findings}
The findings of our user study center on the participants' relationships to the Rewinds generated from their location data compared to the static photos. We focus on the participants' judgments of their Rewinds' memorability, believability, and desirability in comparison to their judgments of the photos paired with the Rewinds (Table \ref{table:Rewindvsphotos}).
%We also discuss the participants' interactions with and reactions to their Rewinds.
The results use data from the user studies conducted with 12 men and 6 women. Half identified themselves as frequent travelers, and half said they were regular GPS users, which we defined as people who use GPS navigation even in locations already familiar to them.
%Half of the participants identified themselves as frequent travelers. Additionally, half of the participants were regular GPS users, which we defined as people who use GPS navigation even in locations already familiar to them.
%We used Chi-squared one-tail test for significance analysis.

@@

\section{Memorability}
Rewinds, and digitally-mediated memories in general, are meant to engage a person's memory. To find out what features make a digital memory memorable, we examined participant responses to whether they were able to remember the location in a photo or recall the trip in a Rewind. Photo memorability is determined by whether or not the participant remembered the location depicted. Because a Rewind contains many locations, it would be unfair to evaluate its memorability based on whether the participant remembers any locations portrayed. So, Rewind memorability is determined by whether the participant remembered and could distinguish the particular trip taken. In this section, we look at differences in photo and Rewind memorability based on our five metrics.

>>>>

% heather - need to be rephrased perhaps? Should we give a high level summary of all the relationships we've found? More analysis to be done for photo vs. videos, another table?
% semantic vs episodic memory
% mention distance categories in the beginning (up up up) + everything else 
\section{Findings}
The findings of our user study center on the participants' relationships to the Rewinds generated from their location data compared to the static photos. We focus on the participants' judgments of their Rewinds' memorability, believability, and desirability in comparison to their judgments of the photos paired with the Rewinds (Table \ref{within-subject-table}).
%We also discuss the participants' interactions with and reactions to their Rewinds.
The results use data from the user studies conducted with 12 men and 6 women. Half identified themselves as frequent travelers, and half said they were regular GPS users, which we defined as people who use GPS navigation even in locations already familiar to them.
%Half of the participants identified themselves as frequent travelers. Additionally, half of the participants were regular GPS users, which we defined as people who use GPS navigation even in locations already familiar to them.
%We used Chi-squared one-tail test for significance analysis.

@@

\subsection{Memorability}
Rewinds, and digitally-mediated memories in general, are meant to engage a person's memory. To find out what features make a digital memory memorable, we examined participant responses to whether they were able to remember the location in a photo or recall the trip in a Rewind. Photo memorability is determined by whether or not the participant remembered the location depicted. Because a Rewind contains many locations, it would be unfair to evaluate its memorability based on whether the participant remembers any locations portrayed. So, Rewind memorability is determined by whether the participant remembered and could distinguish the particular trip taken. In this section, we look at differences in photo and Rewind memorability based on our five metrics.
